Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-17 paper/paper.tex
Related work

The problem was studied under resource augmentation \cite{repartition-disc}, and under stochastic assumptions of input\maciek{cite}.\maciek{cite other papers that cite DISC?}

@@

>>>>

The problem was studied under resource augmentation \cite{repartition-disc}, and under stochastic assumptions for the input\cite{stochastic-ring}.
For clusters of size $2$ (i.e., $k=2$), a constant competitive algorithm exists~\cite{repartition-disc}.

@@

The adversary constructs components of nodes, and $\OPT$ never splits them.
The adversary observes the actions of an online algorithm, and if it splits the components at any moment, the adversary issues
